Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-09-01 paper/ms.tex
update ms

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field topologies dominated by
      high order multipoles.  The bottom row compares the latter
      systems against the ``best-matching'' CR light curves, selected
      by eye from Figure~\ref{fig:cqvs}.  CRs have light curves that
      are visually similar to the topologically complex magnetic B
      stars.  Stellar masses rounded to one significant figure are
      given in the lower right of each panel; the star, TESS sector,
      and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

Two interesting and possibly telling exceptions to the rule that
magnetic B stars have simple light curves are HD~37776 and HD~64740.
Both stars are known from spectropolarimetry to have field geometries
dominated by high order multipoles \citep{2011ApJ...726...24K}.
And, recent TESS light curves of these two B stars appear surprisingly
similar to the CR light curves \citep{2020pase.conf...46M}.  The
middle row of Figure~\ref{fig:bstar} shows the phased TESS light
curves for these two stars, with by-eye best-matching CRs shown
underneath for comparison.  The number of dips per cycle, the shapes
of the dips, and the dip depths relative to the sinusoidal envelope
are all similar.  This connection suggests that the highly structured
light curves of both the M dwarfs and the B stars are associated with
(and perhaps caused by) strong non-dipolar magnetic fields.
Non-dipolar fields for M dwarfs are plausible, given that Zeeman
Doppler Imaging has revealed non-axisymmetric magnetic field patterns
for the few M dwarfs for which this technique is technically feasible
\citep[see][and references therein]{2021A&ARv..29....1K}.

>>>>

		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B star connection.}
      $\sigma$~Ori~E and HD~345439 (top row) are magnetic B stars with
      predominantly dipolar magnetic fields known to host
      circumstellar plasma tori.  HD~37776 and HD~64740 (middle row)
      are analogous magnetic B stars with field topologies potentially dominated by
      high order multipoles.  The bottom row compares the latter
      systems against the ``best-matching'' CR light curves, selected
      by eye from Figure~\ref{fig:cqvs}.  CRs have light curves that
      are visually similar to the topologically complex magnetic B
      stars.  Stellar masses rounded to one significant figure are
      given in the lower right of each panel; the star, TESS sector,
      and period are listed in each subtitle.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}

@@

Two interesting and possibly telling exceptions to the rule that
magnetic B stars have simple light curves are HD~37776 and HD~64740.
HD~37776 is known from spectropolarimetry to have an extreme field
geometry dominated by high order multipoles
\citep{2011ApJ...726...24K}.  The field geometry of HD~64740, while
potentially less extreme, is also less well-studied
\citep[see][Ch.~4]{1988PhDT........53B}.  Recent TESS light curves
of these two B stars appear surprisingly similar to the CR light
curves \citep{2020pase.conf...46M}.  The middle row of
Figure~\ref{fig:bstar} shows the phased TESS light curves for these
two stars, with by-eye best-matching CRs shown underneath for
comparison.  The number of dips per cycle, the shapes of the dips, and
the dip depths relative to the sinusoidal envelope are all similar.
This connection suggests that the highly structured light curves of
both the M dwarfs and the B stars are associated with (and perhaps
caused by) strong non-dipolar magnetic fields.  Non-dipolar fields for
M dwarfs are plausible, given that Zeeman Doppler Imaging has revealed
non-axisymmetric magnetic field patterns for the few M dwarfs for
which this technique is technically feasible \citep[see][and
references therein]{2021A&ARv..29....1K}.
